% Intended LaTeX compiler: pdflatex
\documentclass[article,letterpaper,times,10pt,listings-bw,microtype]{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[onehalfspacing]{setspace} \usepackage[T1]{fontenc} \usepackage{mathpazo} \usepackage[scaled=0.85]{helvet} \usepackage{courier} \usepackage{geometry} \geometry{left=1in,right=1in,top=1in,bottom=1in} \usepackage[framemethod=default]{mdframed}
\author{Your Name Joon Ro}
\date{Fall 2018}
\title{ORG 0000-01 Syllabus}
\hypersetup{
 pdfauthor={Your Name Joon Ro},
 pdftitle={ORG 0000-01 Syllabus},
 pdfkeywords={},
 pdfsubject={Fall 2018 Org-Coursepack School specific teaching materials},
 pdfcreator={Emacs 26.1 (Org mode 9.1.14)}, 
 pdflang={English}}
\begin{document}

\definecolor{SchoolColor}{RGB}{70,130,180}

\begin{center}
{\color{SchoolColor}{\Large
\textbf{Journal of Open Source Education}
}}
\end{center}

\begin{center}
{\color{SchoolColor}{
\textbf{ORG 0000-01}

\textbf{Org-Coursepack}

\textbf{Fall 2018}
}}
\end{center}

\vspace{5 mm}

\begin{center}
\begin{tabular}{llll}
\textbf{Instructor:} & Joon H. Ro \& Jae-Eun Namkoong & \textbf{Office Phone:} & (000) 000-0000\\
\textbf{Office:} & BLDG 100 & \textbf{E-mail:} & joon.ro@outlook.com\\
\textbf{Office Hours:} & Tue 3:30-4:30pm & \textbf{Course Site:} & \textbf{\href{https://github.com}{github.com}}\\
\textbf{Class Meeting Day \& Time:} & Tue/Thurs, 9:30a-10:45 & \textbf{Class Location:} & BLDG 100\\
\end{tabular}
\end{center}
\section*{Course Description}
\label{sec:orgbac35d1}
This course provides students with Org-Coursepack, a modular and reusable
teaching materials template in org-mode. Using self-explanatory course
contents, students will be able to adapt the template and create their on
course contents through Org-mode.
\section*{Course Prerequisites}
\label{sec:org8803189}
\begin{itemize}
\item Basic knowledge about using Emacs
\item Basic knowledge about org-mode
\end{itemize}
\section*{Student Learning Objectives}
\label{sec:orgb052fde}
As the result of this course, students should be able to:

\begin{itemize}
\item Adapt Org-Teaching-Template to create their own course contents
\end{itemize}
\section*{Course Material}
\label{sec:org4844ba4}
\begin{description}
\item[{Documentation}] Handouts, readings, and assignments will be uploaded to
the repository.
\item[{Software}] \quad 

\begin{itemize}
\item Emacs. (Orgmode is a built-in package of Emacs)
\item org-reveal
\end{itemize}
\end{description}
\section*{Grading}
\label{sec:org243d2a2}

\subsection*{Grade Basis}
\label{sec:org97d536f}
\begin{center}
\label{tab:orgb6b59c7}
\begin{tabular}{ll}
\hline
Item & Percentage Worth\\
\hline
\textbf{Individual Assessment} & \\
Exam 1 & 18\%\\
Exam 2 & 18\%\\
Final Exam & 29\%\\
In-class Exercise and Participation & 5\%\\
Class Attendance & See below\\
\textbf{Subtotal} & \textbf{70\%}\\
\hline
 & \\
\textbf{Group Assessment} & \\
Assignments & 20\%\\
Presentation & 10\%\\
\textbf{Subtotal} & \textbf{30\%}\\
\hline
 & \\
\textbf{Total} & \textbf{100\%}\\
\hline
\end{tabular}
\end{center}
\subsection*{Individual Assessment}
\label{sec:orgfd25c99}
\subsubsection*{Exams}
\label{sec:org96860af}
All exams are closed-book. Exams 1 and 2 each covers a subsection of the
course material. The final exam will be cumulative. Exams will be held in the
classroom on the following dates:

\begin{description}
\item[{Exam 1}] \textit{2018-02-27 Tue}, in class
\item[{Exam 2}] \textit{2018-03-22 Thu}, in class
\item[{Final Exam}] \textit{2018-12-16 Sun 13:00 } \emph{- 4:00PM}
\end{description}
\subsubsection*{In-Class Exercises and Participation}
\label{sec:org44289c1}
\begin{description}
\item[{Exercises}] Description of exercises

\item[{Participation}] Description of participation here
\end{description}
\subsubsection*{Class Attendance}
\label{sec:orga8e4118}
Attendance at all class sessions is expected.
\subsection*{Group Assessment}
\label{sec:orgce26979}
Description of group assessment
\subsubsection*{Assignments}
\label{sec:org19c84cc}
Description of assignments
\subsubsection*{Presentation}
\label{sec:org622d00f}
Description of presentation
\subsection*{Grade Cutoff Percentage}
\label{sec:org087cdd8}
The following table provides the preliminary guidelines for assigning your
letter grade:

\begin{center}
\begin{tabular}{llllllllllll}
\hline
Grade & A & A- & B+ & B & B- & C+ & C & C- & D+ & D & D-\\
\hline
Cutoff Pct & 93\% & 90\% & 87\% & 83\% & 80\% & 77\% & 73\% & 70\% & 67\% & 63\% & 60\%\\
\hline
\end{tabular}
\end{center}
\section*{Specific Course Policies}
\label{sec:org88f7f98}
Specific Course Policies here.
\section*{School-Specific Policies}
\label{sec:org9fe0e92}
School-specific policies here.
\clearpage
\section*{Class Schedule}
\label{sec:org6cf35ec}
\begin{center}
\begin{tabular}{lrl}
Date & Class & Topic\\
\hline
\textit{2018-08-28 Tue} & 1 & Course Introduction\\
\textit{2018-08-30 Thu} & 2 & Org Mode Basics\\
\textit{2018-09-04 Tue} & 3 & Topic and Course Org Files\\
\textit{2018-09-06 Thu} & 4 & Creating Content for Slides and Handouts\\
\textit{2018-09-11 Tue} & 5 & Exporting Slides and Handouts\\
\textit{2018-09-13 Thu} & 6 & Semester Org Files (1/4): Introduction\\
\textit{2018-09-18 Tue} & 7 & Semester Org Files (2/4): Sections and Syllabus\\
\textit{2018-09-20 Thu} & 8 & Semester Org Files (3/4): Lectures\\
\textit{2018-09-25 Tue} & 9 & Semester Org Files (4/4): Exams and Assignments\\
 &  & \uline{Assignment 1 Due}\\
\textit{2018-09-27 Thu} & 10 & \uline{Mid-Term Exam}\\
\textit{2018-11-21 Wed--2018-11-25 Sun} &  & \textbf{Thanksgiving Holiday}\\
\textit{2018-12-16 Sun 13:00 } \emph{- 4:00PM} &  & \uline{Final Exam}\\
\end{tabular}
\end{center}

\begin{mdframed}[style=exampledefault, frametitle={Disclaimer}]
\begin{itemize}
\item The class schedule is subject to change (except for the exam dates)
\end{itemize}
\end{mdframed}
\end{document}